Analyze Stop Data

### 2016-07-29 AnalysizeStop.Rmd
07292016

#Sample graph
stop_race <- ggplot(stop_by, aes(x = Race, fill = Gender)) + 
  geom_bar(aes(y = ..count../sum(..count..))) + 
  labs(y = "Density") +
  facet_wrap(~Reason)

>>>>

#Sample graph
stop_race <- ggplot(stop_by, aes(x = Race, fill = Gender)) + 
  geom_bar(aes(y = ..count../sum(..count..))) + 
  scale_fill_manual(values = c("skyblue1", "pink")) +
  labs(y = "Density") +
  facet_wrap(~Reason)

#Gender, race, and enforcement
